Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-04-02 paper.tex
update

The \emph{semantic matchmaking quality} of the service composition can be obtained by aggregating over all edges in $E$ as follows:
%\begin{equation}
%\label{eqSM}
%SM \stackrel{.}{=} (MT, SIM)
%\end{equation}
\vspace{-0.2cm}
\begin{equation}
\label{equation6}
MT {=} \prod_{j=1}^{m} type_ {e_{j}}
\end{equation}
\begin{equation}
\label{equation7}
SIM {=} \frac{1}{m}\sum_{j=1}^m sim_ {e_{j}}
\end{equation}
%\begin{equation}
%\label{eqCQ}
%CQ \stackrel{.}{=} (MT, \  SIM, \  A,\  R,\  C,\  T)
%\end{equation}
The \emph{QoS} of the service composition can be obtained by aggregating the QoS values of the participating services. For a service composition with services $ S_1, S_2, ... S_n$ we obtain the reliability $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consumption path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $P_j$ is a path of length $\ell_j$}\}.$$

@@

To analyse the effectiveness of achieving a good comprehensive quality at the expense of slightly reduced QoS, we demonstrate two best solutions produced using task 3 as an example. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two $WGs$ as the best solutions obtained by employing the QoS model and the comprehensive quality model respectively. Both $WGs$ have exactly the same service workflow structure, but some service vertices and edges denoted in red are different. To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to each edge in Fig. \ref{comparisontest} $(3)$ (Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality model. Therefore, we achieve an overall gain 0.1433, which is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034). To understand the improvement of semantic matchmaking quality from these numbers, we pick up $e_4$ that is associated with the smallest $\Delta Q$. The $e_4$ of Fig. \ref{comparisontest} $(1)$ and Fig. \ref{comparisontest} $(2)$ has two different source service vertices, $Ser1640238160$ and $Ser947554374$, and two same $end$ vertices. $Ser1640238160$ and $Ser947554374$ are services with output parameters $Inst582785907$ and  $Inst795998200$ corresponds to two related concepts $Con2037585750$ and $Con103314376$ respectively in an ontology shown in Fig. \ref{comparisontest} $(4)$. As $Inst658772240$ is a required parameter of the $end$, and related to concept $Con2113572083$, $Inst795998200$ is closer to the required output $Inst658772240$ compared to $Inst582785907$. Therefore,  $Ser947554374$ is selected with a better semantic matchmaking quality compared to $Ser1640238160$.

>>>>

The \emph{semantic matchmaking quality} of the service composition can be obtained by aggregating overall edges in $E$ as follows:
%\begin{equation}
%\label{eqSM}
%SM \stackrel{.}{=} (MT, SIM)
%\end{equation}
\vspace{-0.2cm}
\begin{equation}
\label{equation6}
MT {=} \prod_{j=1}^{m} type_ {e_{j}}
\end{equation}
\begin{equation}
\label{equation7}
SIM {=} \frac{1}{m}\sum_{j=1}^m sim_ {e_{j}}
\end{equation}
%\begin{equation}
%\label{eqCQ}
%CQ \stackrel{.}{=} (MT, \  SIM, \  A,\  R,\  C,\  T)
%\end{equation}
The \emph{QoS} of the service composition can be obtained by aggregating the QoS values of the participating services. For a service composition with services $ S_1, S_2, ... S_n$ we obtain the reliability $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consumption path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $\ell_j$ is the length of a path $P_j$}\}.$$

@@

To analyse the effectiveness of achieving a good comprehensive quality at the expense of slightly reduced QoS, we demonstrate two best solutions produced using task 3 as an example. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two $WGs$, $WG_1$ and $WG_2$ as the best solutions obtained by employing the QoS model and the comprehensive quality model respectively. Both $WGs$ have exactly the same service workflow structure, but some service vertices and edges denoted in red are different. To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to these different edges in $WG_1$ and $WG_2$. \ref{comparisontest} $(3)$ (Note: $sm_{e_n} = 0.5type_{e_n} + 0.5 sim_{e_n}$), where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality model. Therefore, we achieve an overall gain 0.1433, which is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034). To understand the improvement of semantic matchmaking quality from these numbers, we pick up $e_4$ that is associated with the smallest $\Delta Q$. The $e_4$ of $WG_1$ and $WG_2$ has two different source service vertices, $Ser1640238160$ and $Ser947554374$, and two the same $end$ vertices. $Ser1640238160$ and $Ser947554374$ are services with output parameters $Inst582785907$ and  $Inst795998200$ corresponds to two concepts $Con2037585750$ and $Con103314376$ respectively in the given ontology shown in Fig. \ref{comparisontest} $(4)$. As $Inst658772240$ is a required parameter of the $end$, and related to concept $Con2113572083$, $Inst795998200$ is closer to the required output $Inst658772240$ compared to $Inst582785907$. Therefore,  $Ser947554374$ is selected with a better semantic matchmaking quality compared to $Ser1640238160$.
